Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-24 Docs/Paper/LaTex/template.tex
Translated Edilson's text and implemented Lucas's comments

%----------------------------------------------
\subsection{OpenMP}
\label{OpenMP}
%----------------------------------------------
The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages. OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows. OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms. In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}

@@

\textcolor{blue}{Nao existem outras diretivas? Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao. Foi somente o ``\#pragma omp parallel for''??}

@@

In the above example, the for loop is executed in parallel \textcolor{blue}{Como? Cada posicao do array eh executada em um nucleo diferente?}. Each iteration of the loop is executed in a separated thread.

@@

\textcolor{blue}{Mover este texto para a secao de background sobre OpenMP?... OpenMP is a standard Application Programming Interface (API) for shared memory programming, which has been very successful for structural parallelism in applications. The API provides a directive-based programming approach to write parallel versions of C/C++ programs ~\cite{Qawasmeh2014}.}

As described in Section~\ref{OpenMP}, in OpenMP the implementation is based on the fork-join model. The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads. After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
	\caption{ESBMC Multi-core.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

@@

\textcolor{blue}{Precisas descrever no topo do algoritmo as entradas e saidas}

@@

\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS.}

\begin{itemize}
\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
\item{\textbf{ESBMC-MC:} This uses a sequential strategy $\left\{1,2,\ldots, H_{max}\right\}$; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}
\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
\end{itemize}

@@

\textcolor{Red}{A ferramenta vZ ~\cite{Bjorner2014} e ~\cite{Bjorner2015} oferece ganhos substanciais em problemas de otimizacao. O trabalho descrito em ~\cite{Pavlinovic2015} relata erros em compiladores e suas confusas mensagens, a abordagem classica é mostrar ao programador qual o local de erro e um dica sobre o mesmo, entretanto, outras fontes de erros não são consideradas, a abordagem mais indicada seria considerar todas as fontes de erros possiveis. Para modelar o problema são geradas as restricoes usando EasyOCaml, e vZ é responsavel por computar a menor caminho de erros. o Algoritmo descrito em ~\cite{Pavlinovic2015} mostrou-se eficiente frente as outras abordagens.}

\textcolor{Red}{O problema abordado neste trabalho utiliza objetivo unico, minimizacao da funcao objetivo, em ~\cite{Patrick2015} é comparada as ferramentas OptiMathSAT com vZ para problemas de verificacao de SW. OptiMathSAT usando multiplos objetivos funciona muito melhor do que vZ com mulitplos objetivos, contudo, para problemas com objetivos unicos vZ se comparta melhor do que OptiMathSAT.}

>>>>

%----------------------------------------------
\subsection{OpenMP}
\label{OpenMP}
%----------------------------------------------
The OpenMP is a set of directives for parallel programming that augments C/C$++$ and Fortran languages. OpenMP supports most processor architectures and operating systems, e.g., Solaris, AIX, HP-UX, Linux, Mac OS X, and Windows. OpenMP uses a portable and very robust model that makes easy for programmers to develop parallel applications for a variety of platforms.

In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}. The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads. After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.

@@

\textcolor{blue}{Nao existem outras diretivas? Explicar um pouco mais sobre o OpenMP, em especial, tente descrever as funcoes que usamos na nossa solucao. Foi somente o ``\#pragma omp parallel for''??. Professor, usei tambem regiao critica}

@@

In the above example, the for loop is executed in parallel \textcolor{blue}{Como? Cada posicao do array eh executada em um nucleo diferente? Não é garantido que use. Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}. Each iteration of the loop is executed in a separated thread. \textcolor{red}{Each thread may use an idle processor}.

There is also a way to specify critical regions, which is a block of code that is guaranteed to be execute by a single thread at a time. To create a critical region   the directive ``\#pragma omp critical'' should be used.

@@

Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.pdf} 
	\caption{ESBMC Multi-core.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Workers}
\label{Multi-core-ESBMC-with-OpenMP-using-workers}
%----------------------------------------------

@@

\textcolor{blue}{Precisas descrever no topo do algoritmo as entradas e saidas}
\textcolor{red}{The algorithm below is called from each worker in order to get the next step to execute if it exists, if not, zero or a negative number will be returned.}

@@

\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS. Feito}

\begin{itemize}
\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
\item{\textbf{ESBMC-MC:} This uses a sequential strategy $\left\{1,2,\ldots, H_{max}\right\}$; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
\end{itemize}

@@

\textcolor{Red}{The vZ tool ~\cite{Bjorner2014} and ~\cite{Bjorner2015} offer substantial improvements on optimization problems. The work described in ~\cite{Pavlinovic2015} reports compiler errors and its confuse messages, the classic approach is to show to the programmer the error location and a hint about it, however, another error sources are not considered, the most appropriate approach would be to consider all possible error sources. To model the problem the restrictions are generated using EasyOCaml, and vZ is responsible to compute the best error path. The algorithm described in ~\cite{Pavlinovic2015} shows efficient against the other approaches.}

\textcolor{Red}{The problem adressed in this work uses a single objective, minimizing of the objective function, in ~\cite{Patrick2015} is compared the tools  OptiMathSAT and vZ for software optimization problems. OptiMathSAT using multiple objectives works way better than vZ, however, for problems with single objectives vZ behaves better than OptiMathSAT.}
